---
title: "Simulation"
output: html_document
---
#Synopsis
We will investigate the exponential distribution in R and compare i twith the Central Limit Theorem.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We run 1000 simulations on generating 40 random numbers from a exponential distribution with lamda value = 0.2. The result is saved to a matrix, called sim, and each row of sim is one simulation. So the sim has 1000 rows and 40 columns.

```{r}
n <- 40
lambda <- 0.2
n.of.sim <- 1000
sim <- matrix(sapply(1:n.of.sim, function(i){rexp(n,lambda)}), n.of.sim,n)
dim(sim)
```
We calculate the means of each row and save the vector of means to variable means.

```{r}
means <- apply(sim, 1, mean)
hist(means, breaks=40)

mean.of.sim = mean(means)
sd.of.sim = sd(means)
pop.sd = sd.of.sim * sqrt(n)

```
**Mean of simulated sample means: `r mean.of.sim`**

**SD of simulated sample means: `r sd.of.sim`**

**SD of population: `r pop.sd`**

**Theoretical mean: `r 1/lambda`**

**Theoretical SD: `r 1/lambda`**