---
title: "final_growth"
author: "Author: Joohyun Kwon"
---

## Overview of ToothGrowth Data

Load library (ggplot2, datasets) and load ToothGrowth data
```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(datasets)
data(ToothGrowth)
```

```{r cache=TRUE}
head(ToothGrowth)
tail(ToothGrowth)
str(ToothGrowth)
summary(ToothGrowth)
unique(ToothGrowth$dose)
```

The supp column is a factor and has two levels - VC and OJ. The dose column is numeric but has only 3 different values (0.5, 1, 2.0). So we can take this column as factor too.

## Exploration

We will start by examing impact of each supplement by its dosage. Multipanel boxplot (by supplement) will provide a good glimpse on the data.

```{r cache=TRUE}
g <- ggplot(ToothGrowth, aes(x=factor(dose),y=len, fill=factor(dose)))
g + geom_boxplot() + facet_grid(.~supp)
```

The boxplot show that OJ yield higer growth in lower dosage than VC. However, VC growth increases more as the dosage increases. OJ's growth is not increasing so much as VC's, as the dosage increase. Also. OJ seems to have higher variance in the lower dosage than VC. However, VC seems to have higher variance in the highest dosage.

We will test a null hypothesis that the impact of dosage increase of OJ to tooth lengh is equal to that of VC. Here, based on previous overview, we will propose an alternative hypothesis where the impact of VC is larger than that of OJ to tooth growth. For this, we will compare mean differences of 0.5 and 2 dose between OJ and VC.

```{r}
oj <- ToothGrowth[ToothGrowth$supp =="OJ",]
vc <- ToothGrowth[ToothGrowth$supp =="VC",]
oj.i <- ToothGrowth[ToothGrowth$supp == "OJ" & ToothGrowth$dose == .5,]$len
oj.f <- ToothGrowth[ToothGrowth$supp == "OJ" & ToothGrowth$dose == 2,]$len
vc.i <- ToothGrowth[ToothGrowth$supp == "VC" & ToothGrowth$dose == .5,]$len
vc.f <- ToothGrowth[ToothGrowth$supp == "VC" & ToothGrowth$dose == 2,]$len
```

